---
title: 'STAT 140: Homework 6'
subtitle: 'Sections 3.5, 4.1'
author: "YOUR NAME HERE"
date: "3/13/2020"
output:
  pdf_document: default
---

## BOOK EXERCISES (OpenIntro Statistics, Fourth Edition)

#### 4.1) **Area under the curve, Part I.** What percent of a standard normal distribution $N(\mu=0,\sigma=1)$ is found in each region? For each part, draw a picture, use appropriate probability notation, and show all your work. You can use R.

a) Z < -1.35

**Draw a picture.**

**Answer.**

```{r}

```


b) Z > 1.48

**Draw a picture.**

**Answer.**

```{r}

```


c) -0.4 < Z < 1.5

**Draw a picture.**

**Answer.**

```{r}

```


d) |Z| > 2 (|Z| means the absolute value of Z. We can rewrite this question as Z > 2 or Z < -2.)

**Draw a picture.**

**Answer.**

```{r}

```


#### 4.2) **Area under the curve, Part II.** What percent of a standard normal distribution is found in each region? For each part, draw a picture, use appropriate probability notation, and show all your work. You can use R.

a) Z < -1.13

**Draw a picture.**

**Answer.**

```{r}

```


b) Z < 0.18

**Draw a picture.**

**Answer.**

```{r}

```

c) Z > 8

**Draw a picture.**

**Answer.**

```{r}

```


d) |Z| < 0.5

**Draw a picture.**

**Answer.**

```{r}

```


#### 4.7) **LA weather, Part I.** The average daily high temperature in June in LA is 77 degrees Fahrenheit with a standard deviation of 5 degrees. Suppose that the temperatures in June closely follow a normal distribution.

a) What is the probability of observing an 83 degree Fahrenheit temperature or higher in LA during a randomly chosen day in June? Draw a picture, use appropriate probability notation, and show all your work.

**Draw a picture:**

**Answer:**

```{r}

```


b) How cool are the coldest 10% of the days (days with the lowest average high temperature) during June in LA? Draw a picture, use appropriate probability notation, and show all your work.

**Draw a picture:**

**Answer:**

```{r}

```


#### 4.10) **Find the SD.** Cholesterol levels for women aged 20 to 34 follow an approximately normal distribution with mean 185 milligrams per decileter (mg/dl). Women with cholesterol levels above 220 mg/dl are considered to have high cholesterol and about 18.5% of women fall into this category. What is the standard deviation of the distribution of cholesterol levels for women aged 20 to 34? Draw a picture to help summarize what you know, use appropriate notation, and show all your work. You can use R (it is a calculator, after all!)

**Draw a picture:**

**Answer:**

```{r}

```


#### 4.46) Heights of 10 year olds, Part II. Heights of 10 year olds, regardless of gender, closely follow a normal distribution with mean 55 inches and standard deviation 6 inches. The height requirement for *Batman the Ride* at Six Flags Magic Mountain is 54 inches. What percent of 10 year olds cannot go on this ride? You can use R (it is a calculator, after all!)

```{r}

```


## R EXERCISE

Pizza delivery times are approximately normally distributed, with mean 30 minutes and standard deviation 5 minutes. You will use this information to answer the questions below. This exercise involves as review of the pnorm() and qnorm() functions we saw in lecture.

#### What is the probability that delivery takes less than 20 minutes?

```{r}

```


#### What is the probability that delivery takes more than 40 minutes? 

```{r}

```


#### What do you notice about the previous two answers? Why is this happening? (No R required.)

**Answer:**

#### The fastest 15% of deliveries occur in under how many minutes?

```{r}

```


#### Half of the deliveries take more than how many minutes?

```{r}

```


Did you need R to answer the previous question? Why or why not?
